%!TEX root = ../main.tex
%Adding the above line, with the name of your base .tex file (in this case "main.tex") will allow you to compile the whole thesis even when working inside one of the chapter tex files

\begin{acknowledgements}
First of all, I want to thank Prof. Kate Maguire, who has supported me and provided guidance for me to get where I am now. You gave me the freedom to do things my way, and fully supported me every time I decided I wanted to be somewhere else than Dublin. I am extremely grateful for everything you have done to make my multinational journey possible. I like to think that I was still able to do a satisfactory amount of work, given that I now have three more years of working with you to look forward to. I promise I'll be in Dublin a bit more this time around.

I also want to thank the postdocs in the TCD transients group. Georgios Dimitriadis, thank you for your support in getting me into the positions that I did, and thank you for reducing all those IDS spectra for me. Umut Burgaz, thank you for the enlightening conversations we've had, I look forward to working together with you some more. Simon Prentice and Mark Magee, though we never got to work together in person due to (cough) external reasons, I still learned a lot from you and want to thank you for helping me at the start of my PhD.

Then there are the other PhD students in the group, Maxime Deckers and Luke Harvey. Though our paths were destined to diverge at some point, I guess that happened a bit sooner than expected. Still, doing this PhD together with you has truly been delightful. Maxime, I wish you all the best with your family, and make sure to teach them to speak Dutch. Luke, you are proof that the smallest of chance encounters can ignite a runaway process to become the most important thing in life, I wish the two of you all the best in the south of France. At the very least the climate there beats that of Dublin.

Of course I cannot forget the other astronomers at Trinity, my collaborators at the Zwicky Transient Facility, and the people from the PESSTO collaboration. Thank you all for the many enlightening discussions and the amazing opportunities that helped me improve my work in many ways.

I want to thank my friends in La Palma (or wherever you are now), the staff and students from the ING, NOT, and other telescopes of the ORM, for the amazing opportunities these studentships have given me. My time with all of you on this island has changed me forever. You are the greatest group of friends I've ever had, and I'm not just talking about the size. The main reason why I decided to spend half my PhD here is because of all of you. And a special thanks to all of you who generously observed my targets for me: 77 classifications and multiple papers that make use of the data, this would not have been possible without your help.

To my friends back in the Netherlands, Koen, Jesse, Marieke, Yann, we all have chosen very different paths in life, following our own passions and interests. Yet our time together started a friendship that will last a lifetime, even if some of us choose to live on a faraway island (or La Palma).

I never would have started this journey without the everlasting support of my family. Mom, I know you would have preferred me to live closer, but even though the town I grew up in is over the mountain, that mountain does not house the telescopes I need for my work. Thanks for standing by me nonetheless. Dad, your levelheadedness and calm outlook on life is a state of mind I can only strive to achieve. And when I inevitably end up breaking something, you are always there to help fix it. Twan, my big little brother, you are one of my closest friends, and your dry humour can make (or break) my day. Let's play another game sometime. Grandma, it is rare to see someone with such a love for life as you, you are the reason why I'm always up for a stupid idea. And Grandpa, your inquisitive mind shines through in both our conversations and our games of Shogi, and your interest in my work makes you my biggest supporter. Knight to B8. %my replacement move that has a note in our 1-year game

Last but not least, \begin{CJK*}{UTF8}{gbsn}赵尤超\end{CJK*}, though we only met close to the end of this endeavour of mine, you have shown me more love, support, and enthusiasm than I ever could have dreamt of. I look forward to the day when we finally meet in person, and every day after that.

\end{acknowledgements}
